Learning by Teaching a Robot:\\The Case of Handwriting

### 2015-12-11 main.tex
Started to rewrite the Normandy study

To date, the system has been deployed and tested in three different
schools (totalling child-robot interactions with more than 70 children, aged 5
to 8) and we also conducted 2 case studies that lasted several weeks.
Table~\ref{studies} gives an overview of these studies.

\begin{table}[ht!]
\centering
\caption{\small Field studies conducted within the project}
\label{studies}
\footnotesize
\begin{tabular}{@{}lp{4cm}p{2.2cm}p{2cm}l@{}}
\toprule
{\bf Study}     & {\bf Type}                                    & {\bf Avg. duration}              & {\bf Children \#}                     & {\bf Ages} \\ \midrule
{\it ISG 1}     & Unstructured group interaction at school      & 16 min/group               & 4 $\times$ 8 children                 & 6-7        \\
{\it Florimont} & Individual/Pair interaction at school         & 11 min/group               & 7 (individual) + 7 $\times$ 2 (pairs) & 7-8        \\
{\it Vincent}     & Case-study, spanning over 4 weeks              & 1.5h $\times$ 4 weeks & 1                                     & 6          \\
{\it Haut-Lac}  & Pair interaction at school & 26 min/group                            & 7 $\times$ 2                          & 5-6        \\
{\it ISG 2}     & Individual interaction at school              & 18 min                            & 6                                     & 5-6        \\
{\it Thomas}     & Case-study, spanning over 4 weeks              & 1h $\times$ 4 weeks        & 1                                     & 5          \\ \bottomrule
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Studies at School}

@@

@@

\begin{figure}
    \centering
    \subfigure[number 1]{
        \includegraphics[width=6cm]{henry1}
    }
    \subfigure[number 2]{
        \includegraphics[width=6cm]{henry2}
    }
	\subfigure[number 5]{
        \includegraphics[width=6cm]{henry5}
    }
    \caption{\small Improvement of Thomas demonstrations for some numbers: a) drawing the allograph of the number 1, b) the number 2 and c) the number 5. Thomas progressively took care of the demonstrations he was providing to the robot for those numbers. We used for this figure the same metric than the one used for the acceptance algorithm. Distances are normalized with respect to the biggest value. The dashed line correspond to the threshold of robot's acceptance.}

@@

\section{Case study 3: when children evaluate the robot}\label{auto}

\subsection{Context}

Each of previous studies was adapted to individual subjects : we used a special
design for each case in order to sustain the child's engagement.
In our next experiment, we conducted case studies with eight children using a single
design. Those children have in common difficulties to learn
cursive writing but the natures and intensities of those troubles are radically
different from one child to another. Valentine (7 years old), Alexandre (6.5) and
Jonathan (7) are under the care of an
occupational therapist. Enzo (8) and Matenzo (7) are repeating their school year
because of writing. Mona (6) and Adele (8) are bottom of their respective
classes in writing activities. Nathan (7) is under the care of a neurologist, and
has been diagnosed with specific language impairment. All of those children are
expected, given their school level, to know the allographs of
cursive letters.

\subsection{Questions}

The main purpose of this study is to test the ergonomic aspects of CoWriter. When introducing the robot, we did not
provide scenario and gave to children minimal explanations. We then observed how easily children assumed the role of the teacher and how seriously they tried to help the robot.

\subsection{Experimental settings}

This experiment took place in the coffee room of a therapists shared surgery
in Normandy, France. Over two weeks, each child came three time for one-hour
session, except Adele and Mona who did just one session. A facilitator was present to explain the rules of the game and tablet usage. As in the previous experiment, children were provided with two tablets : one to choose a word (or a single letter) to teach, and one
used by both the child and the robot to write. We also provided the allograph's template if the child asked for.

The starting point of the robot's writing was the same for all children: we
used middle point between simple vertical strokes and letters. For this study,
we wanted the robot to be only influenced by the demonstrations provided by the
child, so we did not project allographs in a subspace. The new generated
sample by the robot were calculated as the middle way between demonstration and
last state in Cartesian space.

The robot was programmed to accept all demonstrations, giving to the child the
full responsibility of the teacher.

We added two buttons on the tablet  interface: a green one with a ``thumbs up", and
a red one with a ``thumbs down". Those buttons could be used by children to evaluate the
robot (the green one was for rewards while the red one was for punishment). This
way, we could measure the perception of the robot by the child: the more the
child used evaluation buttons, the more he was playing the teacher, judging the
robot instead of himself. It became possible to estimate if a child is playing
seriously given correlation between his evaluation and robot's actual
progression.

\subsection{Results}

All children maintained their engagement during the whole sessions. They
provided on average 42 demonstrations per session. All children used evaluation
buttons and had preference to reward the robot (in total, 99 rewards and 33
punishments were recorded).

Since sessions took place over only two weeks, we did not studied possible
handwriting remediation in children, but we focused on correlation between the
children's evaluations and the robot's progression.  We estimated the robot's
progression as the difference between a starting score (score of the first
robot's try when children have chosen a new word/letter to work on) and the
current robot's score (after being taught by the child). The score is calculated
as the average of euclidean distance between robot's try and a reference
allograph over all letters of the word. Those references for letter allographs
where drawn by us beforehand, taking inspiration in education.com cursive
letters
template\footnote{\url{http://www.education.com/slideshow/cursive-handwriting-z/}}.
Let $P_i$ be the estimated progression of the robot at time $ i$. Of course, if
the child chose to switch to a new word at time $ j$ , we have $ P_{j}=0$ and
clearly $ P_0=0$.  To measure whether the fact that the child was rewarding the
robot when it was progressing was significant or not, we generated 10000 times
the same number of reward/punishment but accorded at random times. Let $ R_i^n$
be the $n^{th}$ generated evaluation at time $ i$ ($ R_i^n = 0$ if no evaluation
occurred at time $ i$ , $ R_i^n=1$ if a reward occurred at time $i$ and
$R_i^n=-1$ if a punishment occurred at time $i$), and $\overline{R}_i$ be the
actual evaluation at time $i$. For each $n^{th}$ generated sequence of
evaluation, we compute a score of evaluation: $$ S^n = \sum\limits_i{R_i^n
P_i}$$ Then we can estimate the p-value $p$ of the actual score: $$ \overline{S}
= \sum\limits_i{\overline{R}_i P_i}$$ given the distribution of the generated
scores $\left(S^n\right)_n$, which is assumed to be Gaussian:

>>>>

The system has been deployed and tested in several situations: in three
different schools (resulting in relatively short child-robot interactions with
more than 70 children, aged 5 to 8), in the surgery of an occupational
therapist (with 8 children, each interacting several hours with the system),
and for two case studies that each lasted several weeks. Table~\ref{studies}
gives an overview of these studies.

\begin{table}[ht!]
\centering
\caption{\small Field studies conducted within the project}
\label{studies}
\footnotesize
\begin{tabular}{@{}lp{4cm}p{2.2cm}p{2cm}l@{}}
\toprule
{\bf Study}     & {\bf Type}                                    & {\bf Avg. duration}              & {\bf Children \#}                     & {\bf Ages} \\ \midrule
{\it ISG 1}     & Unstructured group interaction at school      & 16 min/group               & 4 $\times$ 8 children                 & 6-7        \\
{\it Florimont} & Individual/Pair interaction at school         & 11 min/group               & 7 (individual) + 7 $\times$ 2 (pairs) & 7-8        \\
{\it Vincent}     & Case-study, spanning over 4 weeks              & 1.5h $\times$ 4 weeks & 1                                     & 6          \\
{\it Haut-Lac}  & Pair interaction at school & 26 min/group                            & 7 $\times$ 2                          & 5-6        \\
{\it ISG 2}     & Individual interaction at school              & 18 min                            & 6                                     & 5-6        \\
{\it Thomas}     & Case-study, spanning over 4 weeks              & 1h $\times$ 4 weeks        & 1                                     & 5          \\
{\it Normandie}     & Individual interactions at surgery               & 1h $\times$ 3 sessions & 8                                     & 6-8          \\ \bottomrule
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{System Validation at Schools}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Study: How Children Take on the Role of a Teacher}\label{normandie}

\begin{inparaenum}
This experiment was conducted to study \item how easily children with actual
deficit take on the role of a teacher, and \item if they engage \emph{seriously}
in this role.
\end{inparaenum}

The experiment took place at the surgery of an occupational therapist in
Normandy, France. Eight children participated, all showing troubles with
handwriting acquisition: Valentine (7 years old), Alexandre (6.5) and Jonathan
(7) are under the care of the occupational therapist. Enzo (8) and Matenzo (7)
are repeating their school year because of writing difficulties. Mona (6) and
Adele (8) are both ranked at the bottom of their respective classes in writing
activities. Nathan (7) is under the care of a neurologist, and has been
diagnosed with specific language impairment. Given their school level, all those
children would be expected to know how to correctly shape cursive letters.

Over a period of two weeks, each child attended three time a one hour long
session, except for Adele and Mona who only attended one session. The
experimenter role was limited to the explaination of the rules of the game and
the basic tablet usage. For this experiment, the children were provided with two
tablets: one to choose the word (or single letter) to teach to the robot, one
used to write. We also provided templates of the cursive letters, where the
children to ask for.

We only provided the children with minimal explanations on the task (they would
have to help the robot to improve its writing style), so as to assess if and how
children would naturally take on the role of the teacher, and how seriously they
engaged into helping the robot.

This assessment was carried through two additional buttons on the tablet: a
green ``thumbs up'' and a red ``thumbs down''. The children were told to use
them to evaluate the robot's improvements (``thumb up'' being a way to give
positive feedback while ``thumb down'' would be convey negative feedback). Our
assessment builds on the hypothesis that the more the child provides feedback to
the robot with the green/red buttons, the more he/she assumes the role of a
teacher. Then, by correlating the feedback with the actual performance of the
robot, we can measure to what extend the child was seriously assuming his/her
role: since the child knows what a correct letter should look like, if his/her
feedback does not correlate with the actual performance, the child was likely
engaged into a playful instead of serious role-playing.

All children maintained their engagement during the whole sessions. They
provided on average 42 demonstrations per session. All children used the
feedback buttons and had preference to give positive feedback the robot (99
``thumb up'' \vs 33 ``thumb down'' were recorded).

As the children participated at most 3 hours of interactions spanning over two
week, we did not attempted to measure possible handwriting improvements by the
children, and instead we focused on the possible correlation between the
children's feedback and the robot's progression.  We estimated the robot's
progression as the difference between a starting score (score of the first
robot's try when children have chosen a new word/letter to work on) and the
current robot's score (after being taught by the child). The score is calculated
as the average of euclidean distance between robot's try and a reference
allograph over all letters of the word. Those references for letter allographs
where drawn by us beforehand, taking inspiration in education.com cursive
letters
template\footnote{\url{http://www.education.com/slideshow/cursive-handwriting-z/}}.
Let $P_i$ be the estimated progression of the robot at time $ i$. Of course, if
the child chose to switch to a new word at time $ j$ , we have $ P_{j}=0$ and
clearly $ P_0=0$.  To measure whether the fact that the child was rewarding the
robot when it was progressing was significant or not, we generated 10000 times
the same number of reward/punishment but accorded at random times. Let $ R_i^n$
be the $n^{th}$ generated evaluation at time $ i$ ($ R_i^n = 0$ if no evaluation
occurred at time $ i$ , $ R_i^n=1$ if a reward occurred at time $i$ and
$R_i^n=-1$ if a punishment occurred at time $i$), and $\overline{R}_i$ be the
actual evaluation at time $i$. For each $n^{th}$ generated sequence of
evaluation, we compute a score of evaluation: $$ S^n = \sum\limits_i{R_i^n
P_i}$$ Then we can estimate the p-value $p$ of the actual score: $$ \overline{S}
= \sum\limits_i{\overline{R}_i P_i}$$ given the distribution of the generated
scores $\left(S^n\right)_n$, which is assumed to be Gaussian:

@@

\begin{figure}
    \centering
    \subfigure[Number ``2'']{
        \includegraphics[width=0.45\linewidth]{henry2}
    }
	\subfigure[Number ``5'']{
        \includegraphics[width=0.45\linewidth]{henry5}
    }
    \caption{\small Improvement of Thomas demonstrations for some numbers: a) drawing the allograph of the number 1, b) the number 2 and c) the number 5. Thomas progressively took care of the demonstrations he was providing to the robot for those numbers. We used for this figure the same metric than the one used for the acceptance algorithm. Distances are normalized with respect to the biggest value. The dashed line correspond to the threshold of robot's acceptance.}

@@
